\chapter{Regression Tests}\label{chap:test}
The \dope{} test suite consists of regression tests. They are run to compare 
the output to previous outputs. This is useful (necessary) after 
changing programming code anywhere in the library. 

\begin{itemize}
\item If a test
succeeds, everything is fine in the library. 
\item If not, you should not
check in your code into \dope{}. 
Please make sure what is going wrong and WHY!
\item 
Every command is computed via a Makefile in the basic example 
directory.
\end{itemize}

\section{Tests with third-party packages}
Please keep in mind that DOpElib does not 
only link to deal.II but also to third party libraries.
If these libraries are not installed, the respective regression tests 
will fail. 

Currently the following examples link to third-party examples:
\begin{itemize}
\item \texttt{OPT/StatPDE/Example6}: IPOPT
\item \texttt{OPT/StatPDE/Example8}: SNOPT
\item \texttt{PDE/StatPDE/Example10}: Trilinos (via deal.II)
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Where can I find the tests}
In each example directory you find a sub directory `Test'. Herein, you find 
the parameter files for meshes (*.inp) and a param file (test.prm).
Moreover, the executable is denoted by `test.sh'. Please make sure, that 
the 
\begin{verbatim}
set never_write_list
\end{verbatim}
contains every possible output
\begin{verbatim}
Gradient;Hessian;Tangent;Residual;Update;Control;State
\end{verbatim}
That means, no solution files are written to the output.
Recall, that we are just interested in terminal output that 
is of course sufficient to verify the things.

Hence, the results directory should be empty
\begin{verbatim}
set results_dir   = ./
\end{verbatim}
The rest in the param file must be identically the same as 
in the dope.prm file in the parent directory. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How to start testing?}
You start testing by typing 
\begin{verbatim}
> ./test.sh Store
\end{verbatim}
in the terminal.

After the run, you have to call 
\begin{verbatim}
> ./test.sh Test
\end{verbatim}
to compare your stored output. Of course, there should be no differences.

The useful point is now the following. After implementation of 
new pieces of code in the DOpE library or in the examples, you can
run 
\begin{verbatim}
> ./test.sh Test
\end{verbatim}
Hereby, you compare your `new' output with the previous stored output.

Attention: After changes you should NOT run again
\begin{verbatim}
> ./test.sh Store
\end{verbatim}
In that case, you overwrite your previous output.
